\documentclass[12]{article}
\begin{document}
\begin{title}
\huge{CONCEPT PAPER }
\end{title}
\maketitle
\author{Emaru Emma	14/U/6225/eve	214016772}
\section{INTRODUCTION}

The government and society of Uganda have for so long had a debate on whether to legalize abortion or not. Due to this dilemma I decided to carry out a research to find out the public’s stand on abortion in order to help the government and legislature come up with a decision that will be welcomed by all stake holders in the nation.

\section{BACKGROUND}
For so long in majority of the societies in Uganda, abortion has been generally looked at as a taboo due to the various misfortunes they believe arise from the act. Due to this situation the majority of the girl child has happened to drop out of school due to these unjustified believes by the society. Many girls in Uganda who have attempted to carry out abortion have done it in a manner that hasn’t been professional and safe. Many of these girls have ended up dying and some becoming barren as per the research that states that over 1500 girls die annually due to abortion related cases. [1] For this reason the research I intend to carry out will help find out if the general public agrees with the legalization of abortion that will save lives if done in a professional and safe manner. This will help the legislature come up with a wise decision on behalf of the girl child in Uganda. This is because over 900,000 of all the 2.2 million pregnancies in the nation are unplanned. [2]

\section{PROBLEM STATEMENT}
Due to the rampant deaths and barrenness that have been caused by abortion that is done in a nonprofessional and unsafe manner, I have decided to carry out a research to find out the general view of the public on the legalization of abortion to save lives and fight barrenness among the girl child. If the public “ s view is positive this will help the legislature come up with a positive legislation that will save the lives of the girl child and also help fight the other complications that arise as a result of unprofessional and unsafe abortion.

\section{OBJECTIVES}

\subsection section{main objective}

To help legalize abortion and save lives and other complications that arise as a result of illegal abortion.

subsection section{specific objective}

To collect data about the general view of the public on the legalization of abortion.


\section{SCOPE}
This research is to be carried about randomly amongst the natives of Uganda and will not involve any other person who is not Uganda.

\section{SIGNIFICANCE}
This research will help the general public and the legislature pass a law that will help save the lives of the girl child who will have to through this unfortunate act and also help them mitigate the side effects of this act.

\end{document}
