\documentclass[10]{article}
\begin{document}


\title{REPORT }
\maketitle
\author{Emaru Emma,14/U/6225/EVE}

\section{INTRODUCTION}

The government and society of Uganda have for so long had a debate on whether to legalize abortion or not. Due to this dilemma I decided to carry out a research to find out the public’s stand on abortion in order to help the government and legislature come up with a decision that will be welcomed by all stake holders in the nation.

\section{BACKGROUND}
For so long in majority of the societies in Uganda, abortion has been generally looked at as a taboo due to the various misfortunes they believe arise from the act. Due to this situation the majority of the girl child has happened to drop out of school due to these unjustified believes by the society. Many girls in Uganda who have attempted to carry out abortion have done it in a manner that hasn’t been professional and safe. Many of these girls have ended up dying and some becoming barren as per the research that states that over 1500 girls die annually due to abortion related cases.[1] For this reason the research I intend to carry out will help find out if the general public agrees with the legalization of abortion that will save lives if done in a professional and safe manner. This will help the legislature come up with a wise decision on behalf of the girl child in Uganda. This is because over 900,000 of all the 2.2 million pregnancies in the nation are unplanned. [2]

\section{OBJECTIVES}

\subsection section{main objective}

To help legalize abortion and save lives and other complications that arise as a result of illegal abortion.

subsection section{specific objective}

To collect data about the general view of the public on the legalization of abortion.


\section{METHODOLOGY}
\subsection{Research questions} 
The questions that were asked are all about abortion as they appear in the forms.
\subsection{Research Design}
The report was written using qualitative methods and specifically using questionnaires as a case study. 
\subsection{Instruments}
This research was conducted using the open Data Kit that was downloaded from play store.

\section{Sample}
The sample information was obtained randomly.
\section{Data collection}
The data was collected using a data collection application download onto the phone.

\section{Data analysis}
This data was analyzed using pi charts.
\section{Limitations}
The sample size used was small.

\section{Recommendations}
Basing on the research finds, I happened to find out that majority of the sample size supported the idea of legalizing abortion in order to prevent to minimize the deaths caused by abortion.
\section{References}

[1] .Chatherine Mwesigwa Kiiza.”New Vision Uganda,” Presented on the 22nd October .coalition to end maternal deaths through unsafe abortion held at Kabira country club in Kampala, 2013.

[2]. Chatherine Mwesigwa Kiiza.”New Vision Uganda,” Presented on the 22nd October .coalition to end maternal deaths through unsafe abortion held at Kabira country club in Kampala, 2013.

\end{document}
